### 2014-02-24 paper/retrofit.tex
temporary clearpage to make things more readable.
Some descriptive text.
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

We consider languages in the form of abstract state machines |(tS, tE,
te, ->)|, where |tS| is the global machine state, |tE| is an evaluation
context, |te| is an expression in the language and |->| is the
reduction relation on such configuration, i.e., $|->| : (|tS| \times
|tE| \times |te|) \rightharpoonup (|tS| \times |tE| \times |te|)$ \Red{This doesn't match the way the evaluation rules are currently done with a frame rule}

To get the flavor for our approach, we will first show how our embedding
works for a simple, ML-like language, with references and general recursion.

@@

Typing judgment: $|tyrule tG tS te tty|$

@@

\begin{figure}
\begin{mathpar}
\inferrule[T-ty-address]
{}
{| tyrule tG tS a (ref (tyLookup tS a)) |}
\end{mathpar}

@@

conf tS te @= iconf iS (fullconf id il tS (iniEt te), ldots)
niconf iS id il ie @= iconf iS (fullconf id il tS (iniEi ie), ldots)
CE[e] -> iconf iS (t, ldots) @= CE[e] .-> iconf iS (sched step (t, ldots))
\end{code}
\caption{IFC grammar.}
\label{fig:ifc-grammar}
\end{figure}

>>>>

While we would like to add information flow control to \emph{any}
language, we will have to make some assumptions about the form of the
target language.  We consider languages whose semantics can be expressed
in the form of abstract machines |(tS, tE, te, ->)|, where |tS| is the
global machine state, |tE| is an evaluation context, |te| is an
expression in the language and |->| is the reduction relation on such
configuration, i.e., $|->| : (|tS| \times |tE| \times |te|)
\rightharpoonup (|tS| \times |tE| \times |te|)$.  Metavariables in this
target language have been colored red.

In Figure~\ref{fig:ml}, we give an example of a standard ML-like
language with mutable references.  These semantics have been prepared
for interoperability in the style of Matthews and Findler~\nocite{}, in
particular, the evaluation rules have been expressed in terms of an
evaluation context $\mathcal{E}_{\tar{\Sigma}}$.  Without the embedding,
this evaluation context is defined as |conf tS te @= tS, tE[ te ]|, but
when we perform the embedding, we will reinterpret the meaning
of this operator, moving .

@@

\Red{Suggestion: Only give the rules for references, because otherwise this is all standard.}

@@

\begin{figure}
Typing judgment: $|tyrule tG tS te tty|$
\begin{mathpar}
\inferrule[T-ty-address]
{}
{| tyrule tG tS a (ref (tyLookup tS a)) |}
\end{mathpar}

@@

conf tS te @= iconf iS (fullconf id il tS (iniEt te), ldots)
niconf iS id il ie @= iconf iS (fullconf id il tS (iniEi ie), ldots)
CE[e] -> iconf iS (it, ldots) @= CE[e] .-> iconf iS (sched step (it, ldots))
\end{code}
\caption{IFC grammar.}
\label{fig:ifc-grammar}
\end{figure}
